More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-05-23 2016-Weak-FH-Bisim/WeakBisim.tex
adding thm weak bisim + corol comp

\title{More equivalences for Open pNets\thanks{This work was partially 
funded by the Associated Team FM4CPS
  between INRIA and ECNU, Shanghai}}
\author{ Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Rabéa}
\institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
}
\date{}                                           % Activate to display a given date or no date

@@

Rabea
\begin{itemize}
\item uniformiser p et P pour les pnets \RAB{Done for definitions 6 and 7. We will chek for lemmas 1 and 2}
\item relectures
\end{itemize}
=== en parallele

@@

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <J,\mathcal{S}_1, s_0,
   \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
   are open automata with identical holes of the same sort.

@@

\noindent{\bf Invisible $\tau$ transitions:}
\begin{mathpar}
 \openrule
         {
           \emptyset,\symb{True},Id(s)}
         {s \OTWeakarrow {\tau} s} \in \WT
 \end{mathpar}
and
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
\\
 \openrule
         {
           \overline{\gamma},\Pred',({x_k\gets e_k})^{k\in K}   }
         {s' \OTWeakarrow {\tau} s''} \in \WT
}
{ \openrule
         {
           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred'\subst{\Post},
				({x_k\gets (e_k\subst \Post)})^{k\in K} } 
         {s \OTWeakarrow {\tau} s''} \in \WT
}
 \end{mathpar}

@@

>>>>

\title{More equivalences for Open pNets\thanks{This work was partially 
funded by the Associated Team FM4CPS
  between INRIA and ECNU, Shanghai}}
\author{ Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Rab\'ea}
\institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
}
\date{}                                           % Activate to display a given date or no date

@@

Rabea
\begin{itemize}
\item [x] uniformiser p et P pour les pnets 
\item [x] relectures
\end{itemize}
=== en parallele

@@

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <\!J,\mathcal{S}_1, s_0,
   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, \mathcal{T}_2\!>$
   are open automata with identical holes of the same sort.

@@

\noindent{\bf Invisible $\tau$ transitions:}
\begin{mathpar}
 \openrule
         {
           \emptyset,\symb{True},Id(s)}
         {s \OTWeakarrow {\tau} s} \in \WT
 \end{mathpar}
and
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
\\
 \openrule
         {
           \overline{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
         {s' \OTWeakarrow {\tau} s''} \in \WT
}
{ \openrule
         {
           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
         {s \OTWeakarrow {\tau} s''} \in \WT
}
 \end{mathpar}

@@

\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
is a weak FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
reflexive, symmetric and transitive.
\end{theorem}

\TODO{We will discuss this corollary and the title.}

\begin{corollary}[Weak Composability]
	Consider two weak FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
	inside those two original pNets, a subset of the holes by FH-bisimilar pNets, we 
	obtain two weak FH-bisimilar pNets.
\end{corollary}
